Self Regulation Ontology Retest Data Report

### 2018-02-18 code/SRO_Report.Rmd
updating report w new data

```{r}
process_boot_df = function(df){
  df = df %>%
  drop_na() %>%
  mutate(dv = as.character(dv),
         icc = as.numeric(as.character(icc)),
         spearman = as.numeric(as.character(spearman)),
         eta_sq = as.numeric(as.character(eta_sq)),
         sem = as.numeric(as.character(sem)),
         partial_eta_sq = as.numeric(as.character(partial_eta_sq)),
         omega_sq = as.numeric(as.character(omega_sq)),
         var_subs = as.numeric(as.character(var_subs)),
         var_ind = as.numeric(as.character(var_ind)),
         var_resid = as.numeric(as.character(var_resid)),
         F_time = as.numeric(as.character(F_time)),
         p_time = as.numeric(as.character(p_time)),
         df_time = as.numeric(as.character(df_time)),
         df_resid = as.numeric(as.character(df_resid)))
  return(df)} 
```

@@

Does this change reliability?

```{r}

```

>>>>

```{r}
process_boot_df = function(df){
  df = df %>%
  drop_na() %>%
  mutate(dv = as.character(dv),
         icc = as.numeric(as.character(icc)),
         spearman = as.numeric(as.character(spearman)),
         pearson = as.numeric(as.character(pearson)),
         eta_sq = as.numeric(as.character(eta_sq)),
         sem = as.numeric(as.character(sem)),
         partial_eta_sq = as.numeric(as.character(partial_eta_sq)),
         omega_sq = as.numeric(as.character(omega_sq)),
         var_subs = as.numeric(as.character(var_subs)),
         var_ind = as.numeric(as.character(var_ind)),
         var_resid = as.numeric(as.character(var_resid)),
         F_time = as.numeric(as.character(F_time)),
         p_time = as.numeric(as.character(p_time)),
         df_time = as.numeric(as.character(df_time)),
         df_resid = as.numeric(as.character(df_resid)))
  return(df)} 
```

@@

```{r}
rm(diff)
```

Does this change reliability? 18/33 of the bootstrapped reliability distributions for the refit hddm drift rates have different means than the reliability distributions using the fullfit drift rates. Only in 7/18 is the refit reliabilities higher.

```{r}
#Compare bootstrapped reliabilities for refits (replaced in boot_df) to bootstrapped reliabilities of full fits
refit_ddm_drift_boot_df = boot_df[boot_df$dv %in% grep('hddm_drift',names(hddm_refits), value=T),]
fullfit_ddm_drift_boot_df = fullfit_boot_df[fullfit_boot_df$dv %in% unique(refit_ddm_drift_boot_df$dv),]

get_t_test_out <- function(df){
  out = data.frame(p.value=NA, mean_x = NA, mean_y=NA)
  mod = t.test(df$icc.x, df$icc.y)
  out$p.value = mod$p.value
  out$mean_x = as.numeric(mod$estimate[1])
  out$mean_y = as.numeric(mod$estimate[2])  
  return(out)
}

refit_ddm_drift_boot_df %>%
  select(X, dv, icc) %>%
  left_join(fullfit_ddm_drift_boot_df[,c('X', 'dv', 'icc')], by = c('X', 'dv')) %>%
  group_by(dv) %>%
  do(get_t_test_out(.)) %>%
  mutate(sig_diff = ifelse(p.value<0.05, 1, 0),
         refit_better = ifelse(mean_x>mean_y,1,0)) %>%
  filter(sig_diff == 1, refit_better == 1)
```
